Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-02 paper_jasa.tex
experiment 3 model results
comment on p-value difference

\begin{table}[hbtp]
\caption{Parameter estimates of model in Equation \ref{eqn:mixed}. Estimates are highly significant with $p$-value $<$  0.0001 for all three experiment data.}
\begin{center}
\begin{tabular}{cr@{.}lcc}
  \hline
 &  \multicolumn{3}{c} {Fixed effect}  & Random effect\\
 \cline{2-4}
 Experiment & \multicolumn{2}{l}{Estimate}  &Std. error & Variance\\
  \hline
  1 & 0&39 & 0.0094 & 0.0080 \\ 
  2 & 1&21 &  0.0197 &  0.0443 \\ 
  3 & 0&31 (Intercept)  &   0.1110 & 0.1407\\ 
     & 0&34 (Slope)    &  0.0581     & \\ 
     &-0&72 (correlation) & & \\
   \hline
\end{tabular}
\end{center}
\label{tbl:model_par}
\end{table}

@@

\green{Something is definitely not right! The code looks like it does actual data p-value - min(null pvalue). But how can you get a difference of 0.8 from this??}

 \green{Is this really pct correct, or 1-pct correct? When there is a big diff in p-value almost no-one gets it right! Maybe it is just a scale issue?} We see that when there is a big difference between the $p$-values observers choose the actual data plot more often.

>>>>

\begin{table}[hbtp]
\caption{Parameter estimates of model in Equation \ref{eqn:mixed}. Estimates are highly significant with $p$-value $<$  0.0001 for all three experiment data.}
\begin{center}
\begin{tabular}{cr@{.}lcc}
  \hline
 &  \multicolumn{3}{c} {Fixed effect}  & Random effect\\
 \cline{2-4}
 Experiment & \multicolumn{2}{l}{Estimate}  &Std. error & Variance\\
  \hline
  1 & 0&39 & 0.0094 & 0.0080 \\ 
  2 & 1&21 &  0.0197 &  0.0443 \\ 
  3 & 0&59 (Intercept)  &   0.1668 & 1.9917\\ 
     & 0&21 (Slope)    &  0.0511     &  0.0245\\ 
     &-0&78 (correlation) & & \\
   \hline
\end{tabular}
\end{center}
\label{tbl:model_par}
\end{table}

@@

\green{Something is definitely not right! The code looks like it does actual data p-value - min(null $p$-value). But how can you get a difference of 0.8 from this??} \blue{It is possible theoretically! Suppose data plot $p$-value is larger than 0.8. Under null hypothesis, $p$-value $\sim U(0,1)$. Thus min(null $p$-value) could close to zero by chance producing this large difference. And this has happened in both experiment 1 and 2.}

 \green{Is this really pct correct, or 1-pct correct? \blue{This is proportion correct}. When there is a big diff in p-value almost no-one gets it right! Maybe it is just a scale issue?} \blue{In fact this is what we expect. If there is large difference that means data plot $p$-value is large while minimum $p$-value is very small. This should lead people to pick the wrong plot. Our minimum $p$-value assumption basically says this fact, right?}. We see that when there is a big difference between the $p$-values observers choose the actual data plot more often.
